Projecting genetic associations through gene expression patterns highlights disease etiology and drug mechanisms

### 2023-06-13 output/latex/manuscript.tex
add author contribution statement and competing interests statements

>>>>

\hypertarget{author-contributions-statement}{%
\subsection{Author contributions statement}\label{author-contributions-statement}}

M. Pividori and C.S. Greene conceived and designed the study.
M. Pividori designed the computational methods, performed the experiments, analyzed the data, interpreted the results, and drafted the manuscript.
C.S. Greene supervised the entire project and provided critical guidance throughout the study.
S. Lu and C. Su performed the CRISPR screen with the supervision of S.F.A. Grant.
All authors revised the manuscript and provided critical feedback.

\hypertarget{competing-interests-statement}{%
\subsection{Competing interests statement}\label{competing-interests-statement}}

No competing interests were declared.
